Shaping strategies and standardisation of faceted spheroids from Qianshangying (North China)

### 2025-06-03 analysis/paper/paper.qmd
editing the text

---
title: "Shaping strategy in core and flake industry：Standardized manufacturing of QSY (North China) faceted spheroids"
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: html
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-dpi: 600
bibliography: references.bib
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: console
---

@@

In this study, the 3d models of the cores were collected and used for morphometric and technological analysis, ~~which not only improved the accuracy of the data but also facilitated scholars to verify and replicate the results~~. Digital data were captured using Artec Spider, and post-processing was carried out with Artec Studio \[version number\]. The 3D scan files and all the R and Python code used in the analyses reported here are openly available online at https://doi.org/xxxx/xxxx/.

@@

# 读取 Excel 文件
file_path <- "E:/Lithic Analysis/QSYSpheroidsStudy/analysis/data/derived_data/flaking_intensity_and_shape.xlsx"
data <- read_excel(file_path)

>>>>

---
title: "Shaping strategies and standardisation of faceted spheroids from Qianshangying (North China)"
institute:
  - fosg:
      name: Formatting Open Science Group
      address: 23 Science Street, Eureka, Mississippi, USA
  - fop: Federation of Planets
title-block-published: "Last updated"  
date: now
date-format: long
format: html
execute:
  echo: true
  warning: false
  message: false
  comment: "#>"
  fig-dpi: 600
bibliography: references.bib
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: console
---

@@

In this study, the 3d models of the cores were collected and used for morphometric and technological analysis. Digital data were captured using Artec Spider, and post-processing was carried out with Artec Studio \[version number\]. The 3D scan files and all the R and Python code used in the analyses reported here are openly available online at https://doi.org/xxxx/xxxx/.

@@

# 读取 Excel 文件
file_path <- here("analysis/data/derived_data/flaking_intensity_and_shape.xlsx")
data <- read_excel(file_path)
